Testing for measurement invariance with respect to an ordinal variable

### 2013-02-25 ordinal/ordinal.Rnw
Additions for ordinal simulations: o Code modifications for new test stats o Changes to code in ordinal.Rnw
Also changed estfun-lavaan.R to match the code that will be incorporated into lavaan.


git-svn-id: svn://svn.r-forge.r-project.org/svnroot/semtools@191 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

## auxiliary code
source("../www/mz-ordinal.R")
## TODO Change this:
source("../sandbox/yves/estfun.R")
source("../www/efpFunctional-cat.R")
source("../www/sim-ordinal.R")

>>>>

## auxiliary code
source("../www/mz-ordinal.R")
## TODO Change this:
source("../www/estfun-lavaan.R")
source("../www/efpFunctional-cat.R")
source("../www/sim-ordinal.R")
